Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-15 paper.tex
finally found solution for UML diagram

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{graphs}
\usetikzlibrary{trees}

@@

\tikzset{
  class/.style={
    rectangle,
    minimum size=1cm,
    thick, draw=black,
    text centered,
    text width=1.75cm,
  }
}

\begin{figure}[H]
\begin{tikzpicture}[
  edge from parent fork down,
  sibling distance=5mm, level distance=20mm, node distance=8mm
  ]
  \node (model) [class] {Model}
      child {node (module ) [class] {Module}
        child {node (strategy) [class,align=center,xshift=-9mm] {Execution\\Strategy}
          child {node(every) [class,xshift=-9mm] {Every}}
          child {node (when) [class,xshift=9mm] {When}}
        }
        child {node [class,xshift=9mm] {function}}
      };
  \node (constant) [class,right=of model] {Constant};
  \node (scope)    [class,left=of strategy] {Scope};
\end{tikzpicture}
\caption{Partial Semantic Model Meta-Model}
\label{fig:meta-model}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{graphs}
\usetikzlibrary{trees}
\usetikzlibrary{arrows}

@@

\tikzset{
  class/.style={
    rectangle,
    minimum size=1cm,
    thick, draw=black,
    text centered,
    text width=1.75cm,
  },
  subclass/.style={thick,draw=black,>=open triangle 60,<-},
  aggregate/.style={thick,draw=black,>=diamond,<-}
}

\begin{figure}[H]
\begin{tikzpicture}[
  edge from parent fork down,
  sibling distance=5mm, level distance=20mm, node distance=8mm
  ]
  \node (model) [class] {Model}
      child {node (module ) [class] {Module} edge from parent [aggregate]
        child {node (strategy) [class,align=center,xshift=-9mm] {Execution\\Strategy} edge from parent [aggregate]
          child {node(every) [class,xshift=-9mm] {Every} edge from parent [subclass]}
          child {node (when) [class,xshift=9mm] {When} edge from parent [subclass]}
        }
        child {node [class,xshift=9mm] {function} edge from parent [aggregate]}
      };
  \node (constant) [class,right=of model] {Constant};
  \node (scope)    [class,left=of strategy] {Scope};

  \draw [thick,>=latex,->] (strategy) -- (scope);
  \draw [aggregate] (model) -- (constant);
\end{tikzpicture}
\caption{Partial Semantic Model Meta-Model}
\label{fig:meta-model}
\end{figure}
